Models of lens candidates from Space Warps CFHTLS

### 2017-03-21 parts/app.tex
feedback JC, fix trivial ones

\begin{figure}
  \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
  \caption{
    Comparison of Einstein radii \ER obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the parametrisation algorythm.
    The parameterized model was generated using princible componant analysis on the ensemble of models.
    The blue dashed line represents a perfect recovery of \ER.
    }
  \label{fig:parameter}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
  \caption{
    Comparison of Einstein radii \ER\ obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the parametrisation algorythm.
    The parameterized model was generated using princible componant analysis on the ensemble of models.
    The blue dashed line represents a perfect recovery of \ER.
    }
  \label{fig:parameter}
\end{figure}

### 2017-03-21 parts/intro.tex
nothing
feedback JC, fix trivial ones

All this motivates using galaxy lenses to study the mutual dynamics of
dark matter and gas in galaxies.  Several studies in recent years have
done so
\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
enlarge the samples from tens of lensing galaxies to thousands.  Doing
so requires both finding more lenses and also modelling their masses.
Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016A&A...592A..75P} and by visual inspection
by citizen-science volunteers in Space~Warps
\citep{2016MNRAS.455.1191M} have, between them, discovered an average
of four lenses per square degree.  So one can be optimistic about
finding many thousands of lenses in the next generation of wide-field
surveys, from the LSST in optical and the SKA in radio on the ground,
and Euclid and WFIRST in orbit.

@@

We characterise each model with seven diagnostics, whose purpose is to
help identify which systems are most probably lenses, and which ones
are likely to be most rewarding for future follow-up observations.
The diagnostics are as follows.

>>>>

All this motivates using galaxy lenses to study the mutual dynamics of
dark matter and gas in galaxies.  Several studies in recent years have
done so
\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
enlarge the samples from tens of lensing galaxies to thousands.  Doing
so requires both finding more lenses and also modelling their masses.
Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016A&A...592A..75P} and by visual inspection
by citizen-science volunteers in Space~Warps
\citep{2016MNRAS.455.1191M} have, between them, discovered an average
of four lenses per square degree, so one can be optimistic about
finding many thousands of lenses in the next generation of wide-field
surveys, from the LSST in optical and the SKA in radio on the ground,
and Euclid and WFIRST in orbit.

@@

We characterise each model with seven diagnostics, grouped into three 
categories, whose purpose is to help identify which systems are most probably 
lenses, and which ones are likely to be most rewarding for future follow-up 
observations. The diagnostics are as follows.

### 2017-03-21 parts/stelmass.tex
feedback JC, fix trivial ones

The stellar masses of the lens galaxies are derived by comparison of
the photometric data with M/L estimates from population synthesis
models.  In principle, a detailed analysis of the spectral energy
distribution is needed to derive accurate stellar masses
\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
estimates to within 0.3\,dex in $\log($M$_s$/M$_\odot)$ can be derived
with a single colour, preferably tracing a rest-frame colour similar
to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}.

In this paper we further simplify the analysis by assuming a
relationship between the apparent total magnitude and stellar mass, at
the redshift of the lens.  For typical stellar population parameters,
the variation of this relation is at most 1\,dex.  A further possible
systematic error is contamination of the light of the lensing galaxy
by the lensed galaxy.  Reducing or eliminating the latter would
require detailed fitting of light distributions for each candidate
%TODO cite Leier et al 2011 \citep{}
,
which we have not yet attempted.  These caveats notwithstanding, it is
still interesting to compare the derived stellar mass with the lensing
mass.

@@

Figure~\ref{fig:stelmass}
shows a comparison of stellar and total masses.  The comparatively
large uncertainty in the stellar mass will be improved in future work
by using available optical and NIR magnitudes to derive more accurate
constrains on the stellar populations.

In addition, we also derive halo masses for the lenses by use of the
standard abundance matching technique, whereby a comparison of the
observed stellar mass function of galaxies with the dark matter halo
mass function from N-body simulations results in a simple relation
between the two. We emphasize that this derivation of halo mass should
be considered an ``average'' estimate, and a significant scatter can
be expected as galaxies with the same stellar mass can be found in
different environments. We refer the reader to \cite{2012MNRAS.424..104L}
for an assessment of the effect of abundance matching on the
derivation of dark matter halo properties in lensing galaxies. We
follow the prescription of \citet{2010ApJ...710..903M}, namely:
\begin{equation}
\begin{aligned}
\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
                                     (\Mhalo/M_1)^\gamma} \\
C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
\beta &= 1.057, \quad \gamma = 0.556.
\end{aligned}
\end{equation}
and define a halo-matching index:
\begin{equation}
\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
\end{equation}
that relates the observed lensing to stellar mass, with the
global ratio expected if the host halo corresponds to the
average value derived by abundance matching. Several cases
for $\haloindex$ can be considered:
\begin{itemize}
\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
  lensing mass.
\item $0 < \haloindex < 1$ is the typical situation, where the lens
  includes stars and dark matter, but not the full halo.
\item $\haloindex = 1$ means that the lens consists of the entire halo.
\item $\haloindex > 1$ is in tension with abundance-matching, because the
  lensing mass exceeds the expected halo mass.
\end{itemize}
This is the last of our model diagnostics, expressing whether the
lensing mass is plausible given the light from the candidate lensing
galaxy.

>>>>

The stellar masses of the lens galaxies are derived by comparison of
the photometric data with M/L estimates from population synthesis
models.  In principle, a detailed analysis of the spectral energy
distribution is needed to derive accurate stellar masses
\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
estimates to within 0.3\,dex in $\log(\Mstel/\Msun)$ can be derived
with a single colour, preferably tracing a rest-frame colour similar
to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}.

In this paper we further simplify the analysis by assuming a
relationship between the apparent total magnitude and stellar mass, at
the redshift of the lens.  For typical stellar population parameters,
the variation of this relation is at most 1\,dex.  A further possible
systematic error is contamination of the light of the lensing galaxy
by the lensed galaxy.  Reducing or eliminating the latter would
require detailed fitting of light distributions for each candidate
\citep[see][]{2011ApJ...740...97L}, which we have not yet attempted.  These 
caveats notwithstanding, it is still interesting to compare the derived
stellar mass with the lensing mass.

@@

Figure~\ref{fig:stelmass}
shows a comparison of stellar and total masses.  The comparatively
large uncertainty in the stellar mass will be improved in future work
by using available optical and NIR magnitudes to derive more accurate
constraints on the stellar populations.

In addition, we also derive halo masses for the lenses by use of the
standard abundance matching technique, whereby a comparison of the
observed stellar mass function of galaxies with the dark matter halo
mass function from N-body simulations results in a simple relation
between the two. We emphasize that this derivation of halo mass should
be considered an ``average'' estimate, and a significant scatter can
be expected as galaxies with the same stellar mass can be found in
different environments. We refer the reader to \cite{2012MNRAS.424..104L}
for an assessment of the effect of abundance matching on the
derivation of dark matter halo properties in lensing galaxies. We
follow the prescription of \citet{2010ApJ...710..903M}, namely:
\begin{equation}
\begin{aligned}
\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/\Mone)^{-\beta} +
                                     (\Mhalo/\Mone)^\gamma} \\
C_0 &= 0.02820, \quad \Mone = 10^{11.884} \Msun \\
\beta &= 1.057, \quad \gamma = 0.556.
\end{aligned}
\end{equation}
and define a halo-matching index:
\begin{equation}
\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
\end{equation}
that relates the observed lensing to stellar mass, with the
global ratio expected if the host halo corresponds to the
average value derived by abundance matching. Several cases
for $\haloindex$ can be considered:
\begin{itemize}
\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
  lensing mass.
\item $0 < \haloindex < 1$ is the typical situation, where the lens
  includes stars and dark matter, but not the full halo.
\item $\haloindex = 1$ means that the lens consists of the entire halo.
\item $\haloindex > 1$ is in tension with abundance-matching, because the
  lensing mass exceeds the expected halo mass.
\end{itemize}
This is the last of our model diagnostics, expressing whether the
lensing mass is plausible given the light from the candidate lensing
galaxy.

### 2017-03-21 parts/summary.tex
feedback JC, fix trivial ones

Figure~\ref{fig:stelmass} is another summary.  It shows most of the
candidates having stellar and total mass typical of massive
ellipticals.  SW05 is the most massive of all the candidates, with a
mass of galaxy-group scale.  It is a particularly attractive system
for follow-up observations at higher resolution, as it large system
with clear multiple-image features, and modelling leaves little doubt
that it is a lens.  The two lowest-mass systems, SW19 and SW42, are
important if they are indeed lenses, because of their low mass.  The
models in both cases are plausible but not entirely satisfactory.

>>>>

Figure~\ref{fig:stelmass} is another summary.  It shows most of the
candidates having stellar and total mass typical of massive
ellipticals.  SW05 is the most massive of all the candidates, with a
mass of galaxy-group scale.  It is a particularly attractive system
for follow-up observations at higher resolution, as it is a large system
with clear multiple-image features, and modelling leaves little doubt
that it is a lens.  The two lowest-mass systems, SW19 and SW42, are
important if they are indeed lenses, because of their low mass.  The
models in both cases are plausible but not entirely satisfactory.
